A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}

### 2022-01-29 ICLP Paper/samplepaper.tex
text on Table 2 revised

    % \\[-2.75mm]
    \botline% \hline
    \end{tabular}
   % }
%    \end{minipage}
% }
%    \hfill\hfill\mbox{~}
\end{table}

@@

Table \ref{tab:Table02} demonstrates the results of the four static decomposition strategies and the machine-based MTWR with the dynamic assignment. Every three sub-columns have illustrated the results of a set of the benchmark instances and each row refers to a decomposition strategy with static (S) or dynamic (D) assignment. The results of this table conclude that the most effective decomposition strategies are machine-based regardless of whether the operations are ordered based on EST or MTWR; however, the dynamic assignment has no positive effect than the static. %The best average makespan of $50\times15$ and $100\times20$ are  $3060.3$, and $5948.6$.
We applied the overlap between the windows to repair the mistakes generated by the decomposition; in addition, we compressed each optimized window to ensure that all the operations had been started as early as possible. Table \ref{tab:Table03} summarizes the results with/without the compression and the overlap. The first column refers to the overlap percentage where $0\%$ means no overlap between TWs. Every three columns have presented the results of a particular set of instances. We applied the overlap and compression with the solutions of the number of windows, which provided a better average makespan using a machine-based EST strategy. In the non-compression part, the overlap has improved the results slightly through the different sizes where $10\%$ and $20\%$ of overlap provided the best results. However, the compression has shown a significant improvement wrt the running time and the average makespan, especially for the $100\times20$ set. The compression demonstrated effectiveness as it minimized the average makespan and decreased the running time compared to the model without compression. Therefore, the overlap and compression have improved the makespan results by $4.5\%, 3.4\%$ and $6.8\%$ and the running time by $40\%$.

>>>>

    % \\[-2.75mm]
    \botline% \hline
    \end{tabular}
   % }
%    \end{minipage}
% }
%    \hfill\hfill\mbox{~}
\end{table}
%
In Table~\ref{tab:Table02}, we compare other problem decomposition strategies
to the static Machine-based EST approach, providing the baseline abbreviated by M-EST.
Further decomposition strategies are denoted by M-MTWR for the static Machine-based MTWR
variant, corresponding dynamic versions M-EST$^\text{\,d}$ and M-MTWR$^\text{\,d}$ that
determine EST and MTWR values w.r.t.\ partial schedules from previous time windows, as well as
static Job-based counterparts J-EST and J-MTWR in the first two rows.
For each decomposition strategy and JSP instance size, we present results for the number
of time windows,
which amounts to the next greater integer of the average number of interrupted optimization
runs in columns headed by Ints, leading to the shortest average makespan.
The considerably increased average makespans in the first two rows clearly indicate that
time windows determined with Job-based decomposition strategies are less adequate than
those investigating bottleneck machines in the first place, and then picking their operations
based on the smallest EST or greatest MTWR value as secondary criterion.
While Machine-based decomposition turns out to be advantageous,
there is no clear gap between the static M-EST and M-MTWR variants as well as their dynamic
versions M-EST$^\text{\,d}$ and M-MTWR$^\text{\,d}$.
That is, the heuristic to schedule operations from highly loaded machines
as soon as possible works well for decomposing the considered JSP instances,
yet further solution quality differences due to minor deviations in the
decomposition strategy or optimization performance of \clingodl are negligible.

@@

% Table \ref{tab:Table02} demonstrates the results of the four static decomposition strategies and the machine-based MTWR with the dynamic assignment. Every three sub-columns have illustrated the results of a set of the benchmark instances and each row refers to a decomposition strategy with static (S) or dynamic (D) assignment. The results of this table conclude that the most effective decomposition strategies are machine-based regardless of whether the operations are ordered based on EST or MTWR; however, the dynamic assignment has no positive effect than the static. %The best average makespan of $50\times15$ and $100\times20$ are  $3060.3$, and $5948.6$.
We applied the overlap between the windows to repair the mistakes generated by the decomposition; in addition, we compressed each optimized window to ensure that all the operations had been started as early as possible. Table \ref{tab:Table03} summarizes the results with/without the compression and the overlap. The first column refers to the overlap percentage where $0\%$ means no overlap between TWs. Every three columns have presented the results of a particular set of instances. We applied the overlap and compression with the solutions of the number of windows, which provided a better average makespan using a machine-based EST strategy. In the non-compression part, the overlap has improved the results slightly through the different sizes where $10\%$ and $20\%$ of overlap provided the best results. However, the compression has shown a significant improvement wrt the running time and the average makespan, especially for the $100\times20$ set. The compression demonstrated effectiveness as it minimized the average makespan and decreased the running time compared to the model without compression. Therefore, the overlap and compression have improved the makespan results by $4.5\%, 3.4\%$ and $6.8\%$ and the running time by $40\%$.
